Interpretable Neural Networks using EAGGA

### 2025-03-15 paper/main.tex
put two figures next to each other

ml.g4dn.xlarge\footnote{2 vCPUs, 16GiB RAM, 1 NVIDIA T4, cf. https://aws.amazon.com/de/ec2/instance-types/g4/} instances with CUDA.

@@

ml.t3.medium\footnote{2 Intel Xeon 8000 vCPUs, 4GiB RAM, cf. https://aws.amazon.com/de/ec2/instance-types/t3/} instances, after which we decided to run the

@@

  \includegraphics[width=0.9\linewidth]{../code/export/plot_test_dhvs.png}
  \label{fig-test-dhvs}

>>>>

ml.g4dn.xlarge\footnote{2 vCPUs, 16GiB RAM, 1 NVIDIA T4, cf. \url{https://aws.amazon.com/ec2/instance-types/g4/}} instances with CUDA.

@@

ml.t3.medium\footnote{2 Intel Xeon 8000 vCPUs, 4GiB RAM, cf. \url{https://aws.amazon.com/ec2/instance-types/t3/}} instances, after which we decided to run the

@@

% have two figures next to each other
\begin{figure}
  \centering
  % make figure wider than textwidth: https://tex.stackexchange.com/a/16584
  \makebox[\textwidth][c]{\begin{minipage}{0.6\linewidth}
      \centering
      \includegraphics[width=\linewidth]{../code/export/plot_test_dhvs.png}
      \caption{Dominated Hypervolume of NNs trained using XGBoost.}
      \label{fig-test-dhvs}
  \end{minipage}\hfill
  \begin{minipage}{0.6\linewidth}
      \centering
      \includegraphics[width=\linewidth]{./EAGGA-XGB-dhv.PNG}
      \caption{Mean dominated Hypervolume of $EAGGA_{\text{XGBoost}}$, $EAGGA_{\text{XGBoost}_{\text{md2}}}$, and union of competitors averaged over
      10 replications. Bars represent standard errors. \citep[Figure 2, p. 544]{EAGGA}}
      \label{fig-eagga-xgb-dhvs}
  \end{minipage}}
\end{figure}
